Stage-Splitting a Modal Language

### 2014-10-09 paper/relatedwork.tex
related work/termination

>>>>

\ur{Umut: I am starting a paragraph on termination.  we might need to expand
  on this.}
\paragraph{Termination.}

There are two reasons for non-termination: infinite loops and
execution of errorneous code.  The splitting algorithm can cause the
first.  But can it also cause the second? (If all computations really
depend on stage 1 code, then would it be possible to for example see
something like 1/0?  i think so but only if there is a meta dependency
between the data in two stages?)

Termination analysis in partial evaluation: see paper~\cite{AH96,GJ05}.
